Cultural evolutionary dynamics with prestige bias

### 2022-12-29 ms/ms.tex
edit intro

\begin{abstract}
A common bias in cultural transmission is to copy whoever appears more successful. This ``success bias'' only depends on the performance of the role-model.
Here, we propose an additional transmission bias that may be common in cultural transmission: ``influence bias'', in which the choice of a role-model depends on the number of individuals that have already copied from that role-model.
We combine success and influence bias together to form a ``prestige bias'', and analyze its effects on cultural-evolutionary dynamics using mathematical analysis and stochastic simulations.
We find analytic approximations to the stochastic role-model choice process, which facilitate further mathematical analysis and reduces the computational complexity of simulations. We validate these approximations using simulations, and demonstrate their robustness to model assumptions.
We also find approximations to the fixation probability and the fixation time of an invading cultural trait, in both constant and changing environments. 
These approximations are similar to Kimura's approximations for population-genetic models.
These similarities show that success bias effectively plays the role of natural selection, whereas influence bias effectively plays the role of genetic drift.

Influence bias also accelerates the evolutionary dynamics, as can be expected in a \textit{rich-getting-richer} process.
Our model extends the literature that attempt to describe of cultural transmission, 
especially in human societies where social media is popular and thus influence bias may be expected. 
Further work is needed to test if this model could predict various phenomena in cultural evolution.
\end{abstract}

@@

\paragraph{Cultural transmission.}
In cultural transmission, individuals transmit cultural traits (i.e., behavior, beliefs, norms) to one another, typically via learning and demonstrating \citep{transmissionVectorsBook}.
Examples for cultural traits in humans are behavioral patterns, such as personalities and habits, transmitted via both verbally and by observations \citep{cultural_traits}.

Although cultural transmission is most common in humans, it is also observed in other animals, e.g., chimpanzees \citep{chimpsPrestige, chimpsCopy}, dolphins and whales \citep{dolphins_whales}, elephants \citep{elepahntsRepo}, and even flies \citep{fliesPaper}.

Cultural transmission may combine vertical transmission, where parents transmit to their offspring; oblique transmission, where adults (teachers, leaders, strangers) transmit traits to unrelated offspring; and horizontal transmission, where peers from the same age cohort transmit to one another. 
Vertical transmission is also possible in the opposite direction: parents may copy traits from their offspring \citep{transmissionVectorsBook,transmissionVectors}.
It has been demonstrated that non-vertical cultural transmission can maintain maladaptive traits, which can be beneficial in changing environments \citep{Ram2018}.

Vertical transmission is also possible in the opposite direction: parents may copy traits from their offspring \citep{transmissionVectorsBook,transmissionVectors}.

Cultural transmission biases may cause a trait to have a disproportionate probability to be transmitted compared to its frequency in the population.
Importantly, even when a trait is disfavored by natural selection, it may still spread in a population due to transmission biases that are strong enough to overcome selection \citep[Ch. 8 pg. 279]{evolutionBook}. 
For example, \citet{cooperation} have shown that helping behaviors can evolve due to horizontal transmission bias even without any benefit to the recipient, or when the benefit is much larger than the cost.

% TODO add definition of success bias and some reference to a study demonstrating it in humans or other animals.
Indeed, in a tournament between learning strategies conducted by \citet{strategiesPaper}, most winner included a mixture of success-biased social learning and individual learning, implying that success-biased learning is a good strategy, but that by itself is not enough, even if success is measured accurately.

\citet[Ch. 5]{evolutionBook} have suggested that the evaluation of success can be divided into three groups: \textit{direct bias}, \textit{indirect bias} and \textit{frequency-dependent bias}.
A direct bias occurs when one phenotype is more attractive than other phenotypes, and is evaluated by \textit{directly} testing the trait.
For example, an individual observing a ping-pong match can attempt both of the observed paddle grips to determine which grip is better.
An indirect bias occurs when an individual uses one phenotype to determine the attractiveness of another phenotype.
For example, an observer may copy the paddle grip of the ping-pong player who scored more points in the match, thus indirectly evaluating the grip by the points scored.
A frequency-dependent bias occurs when the probability to copy a phenotype is higher or lower than the frequency of the phenotype among demonstrators. 
For example, when the common paddle grip is used by 60\% of the demonstrators, then if the probability to copy this grip is 80\%, then transmission is under positive frequency bias, also called conformity; if the probability is 40\%, then transmission is under negative frequency bias, or non-conformity \citep{conformism}. 
The effects of conformity and non-conformity on cultural evolution have been studied with both models \citep{conformity,anticonformity} and experiments \citep{negativeFrequency}.

\paragraph{Prestige.}
Prestige means having a good reputation or high esteem, therefore does not directly signify success, although it may imply it--making it an indirect bias.
\citet[Ch.~8]{evolutionBook} and \citet{complexityPaper} suggest that prestige biases are probably more common in humans than success biases.
\citet[Ch. 8]{evolutionBook} add that maladaptive traits may spread widely in a population if indirect biases are strong enough.
They suggest that such biases could lead to a runaway process caused by a cultural equivalent of sexual selection \citep{sexualSelectionBook}.
On the other hand, \citet{fijian_social_bias} suggest that prestige biases, over generations, can lead to cultural adaptations, and that although prestige can lead to maladaptive traits spreading in the population, it can also accelerate the spread of adaptive traits.
Prestige is often mentioned in the cultural-evolution literature, but seldom modeled.

\paragraph{Influence bias.}
Today, social media provides an easy way to estimate the social and cultural influence individuals have over others, and therefore may have an effect on decision making. Online social networks such as \emph{Facebook} and \emph{Instagram} are known to affect the influence of individuals \citep{social_influence,social_media,influence_analysis}, and specific marketing practices were invented to capitalize on this effect \citep{facebook_marketing}.
Here, we model such influence as an indirect bias in cultural transmission, in which the choice of a role-model depends on the choices made by other individuals that have already chosen a role-model. 
Influence can be easily estimated, so costs may be lower than estimating success. In some cases it could be a more accurate estimation as well.

@@

\subsection*{Dichotomous trait}
To allow for mathematical analysis of the model, we introduce a simplified version where the trait only has two phenotypes: the optimal phenotype $\hat{A}$ and the sub-optimal phenotype $A$. 
All role-models with the same phenotype will contribute to the probability of that phenotype to be transmitted, and thus influence is determined by the number of copiers that have already chosen a role-model with either phenotype.
In addition, we assume homogeneous $\alpha$, also called \textit{exchangability}, for simplicity and for easier mathematical analysis.
Therefore, the probability of the $i$-th copier to copy phenotype $A$ is
\begin{equation}\label{eq:binary-model}
G_{i,A} = \frac{(N-C)\alpha'\beta(A) + K_{i,A}}{i-1 + (N-C)\alpha'\beta(A) + C\alpha'\beta(\hat{A})} = \frac{(N-C)\alpha'\beta(A) + K_{i,A}}{i-1 + (N-C)\alpha'\beta(A) + \alpha'C}
\end{equation}
where $C$ is the number of role-models with trait $\hat{A}$ and $K_{i,A}$ is the number of copiers that already chose $A$ when copier $i$ chooses a role-model and $\alpha'$ is the odd ratio of the bias weight $\alpha'= \frac{\alpha}{1-\alpha}$.

@@

\begin{result}[P{\'{o}}lya urn model]\label{result:polya}
The role-model choice process, $\big\{\vec{K}_i\big\}_{i=1}^N$, is equivalent to a \textit{P\'{o}lya urn model} if both trait estimation error and bias weight are uniform in the population, $e=e_j$ and $\alpha=\alpha_j$ for all $j=1,\ldots,N$.
\end{result}

@@

\citet[section 2]{dirichlet} prove that the proportion of different colored balls in a \textit{P\'{o}lya urn model} converges to the Dirichlet distribution as the number of draws approaches infinity, based on the \textit{Martingale Convergence Theorem} \citep{martingaleBook}.
We therefore have an approximation for the relative prestige each role-model has when evaluated by copiers. Thus, choosing the role-models for all copiers is equivalent to drawing from a Multinomial distribution where the parameters are the modified weights from a Dirichlet distribution and we have the following corollary.
\\

\begin{corollary}\label{cor:dirichlet}
The number of copiers of each role-model follows a Dirichlet-Multinomial distribution, $\vec{K_i} \sim \textit{DM}(N,\vec{G_1})$, under the conditions of \Cref{result:polya}.
\end{corollary}

@@

We ran simulations of the role-model choice process during a single generation in which every copier evaluates its own optimal success-bias weight, $\alpha^*$, which minimizes the expected squared error between the estimated and the ideal trait values,
\begin{equation}
\alpha^* = \textit{argmin} \sum_{j=1}^N\frac{\alpha A_j + (1-\alpha) K_j}{\sum_{l=1}^N\alpha A_l + (1-\alpha) K_l}\cdot (\hat{A}-A_j)^2 \;,
\end{equation}
where $A_j$ is the trait of role-model $j$ and $K_j$ the number of copiers that already chose role-model $j$.

@@

\section*{Discussion}
During cultural transmission, cultural traits such as attitudes, values, beliefs, and behavioral patterns are transmitted between individuals, for example via copying and social learning.
Some cultural traits or cultural role-models may be copied more often due to transmission biases. 
A common bias is success bias, in which copiers are more likely to copy a successful role-model. Many models assume that success can be accurately estimated.
However, it has been suggested that because it is hard to estimate success, a more common bias is \textit{prestige bias}---a bias towards role-models perceived to be successful in other traits \citep{fijian_social_bias}.

@@

According to \citet{animal_leadership}, there are two main approaches to group decision making in nature: leadership and consensus.
Leaders would usually be high-ranking members of the group: elders, individuals with many kin relations, or individuals possessing other dominant traits.
\citet{animal_leadership} describe benefits for the closest associates of a dominant baboon, such as protection from predators. 
In some species, like the females of \textit{Eulemur fulvus rufus} (Red lemur), leaders may arise due to nutritional needs, and not due to possessing superior traits \citep{lemurs}. 
In humans, leadership also has its costs and benefits. Leaders can make decisions that would most benefit them and their closest followers, while still maintaining group cohesion. 
However, wrong decision making that harms the group could result in negative effects for the leader. 
In modern society, many humans strive for prestigious positions, as they may reap rewards greater than the risk and costs to achieve them, or due to individual personality and pressure or education from the family.

\citet{prestige_evolution} suggested that there are two types of leadership: prestige-based and dominance-based leadership.
In the latter, social status is acquired through aggression, intimidation and violence. It is also more common than prestige in non-human animals.
Their definition of prestige seems to overlap with ours. They suggest prestige is composed of estimation in the eyes of other people (similar to our success bias) and commanding position in people's minds, i.e, the number of followers other people think one has, which they define as \textit{influence}, similar to our influence bias.
\citet{prestige_evolution} show that prestige can evolve via natural selection as an efficient process to extract reproductive benefit from the flow of socially transmitted information. They back up their claims by creating testable predictions and using evidence from the literature and experiments of social sciences.
Simply put, prestige can naturally evolve when social learning already exists to save costs of individual learning.

@@

Prestige bias can also accelerate reversal of harmful traditions such as child marriage and domestic violence. 
\citet{harmful_traditions} suggest a \textit{spillover}  mechanism, in which an intervention affects a large enough group in a target population, so that others not included in the intervention also change their behavior.
They found that there are individuals who act as \textit{agents}, who are often looked upon, and therefore they are ideal targets for interventions. This is similar to influential role-models in our model, where a prestigious individual will be copied more often, and will therefore spread his trait faster and wider in the population.
They also suggest a way to use this phenomena to change existing traditions in a population. It is very clear however, that just as it can be used to end harmful traditions, the same agents could start harmful traditions.

\citet{social_brains} hypothesized that larger, more complex brains can store and manage more information and in turn, this information can support the costs of a larger brain.
Following up on this, \citet{collective_brains} offered that prestige can directly affect human physical evolution. They present a concept called \textit{cultural brains}---brains that evolved primarily for the acquisition of adaptive knowledge.
They then develop a model that predicts a strong relationship between brain size and group size, because group size also provides access to more adaptive knowledge. 
They also presented the \textit{cumulative cultural brain} hypothesis, which proposes that human brains have evolved with an ability and tendency for selective, high-fidelity social learning. As part of this process, there are a variety of strategies and biases that have evolved to hone in on the most adaptive knowledge. These strategies and biases include direct and indirect cues of the popularity of cultural traits (e.g. success and prestige biases).
They suggest that one of the reasons for the extreme increase in brain size in humans is the ability to "cheaply" acquire adaptive knowledge via transmission biases such as prestige.

>>>>

\begin{abstract}
A common bias in cultural transmission is to copy whoever appears more successful. This ``success bias'' only depends on the performance of the role-model.
Here, we propose an additional transmission bias that may be common in cultural transmission: ``influence bias'', in which the choice of a role-model depends on the number of individuals that have already copied from that role-model.
We combine success and influence bias together to a ``prestige bias'', and analyze its effects on cultural evolutionary dynamics using mathematical analysis and stochastic simulations.
We find analytic approximations to the stochastic role-model choice process, which facilitate further mathematical analysis and reduce the computational complexity of simulations. We validate these approximations and demonstrate their robustness to model assumptions.
We also find approximations to the fixation probability and the fixation time of an invading cultural trait, in both constant and changing environments. 
These approximations are similar to Kimura's approximations for population-genetic models.
These similarities show that success bias effectively plays the role of natural selection, whereas influence bias effectively plays the role of genetic drift.	
Influence bias also accelerates the evolutionary dynamics, as can be expected in a \emph{rich-getting-richer} process.
Our model extends the literature that describes and analyses cultural transmission, 
especially in human societies where social media is popular and thus influence bias may be expected. 
Further work is needed to test if this model could explain and predict various phenomena in cultural evolution.
\end{abstract}

@@

%\paragraph{Cultural transmission.}
In cultural transmission, individuals transmit cultural traits (i.e., behaviors, beliefs, norms) to one another, typically by learning and demonstrating \citep{transmissionVectorsBook}.
Examples for cultural traits in humans are norms, preferences, tools, ideas, and language, potentially transmitted verbally and/or by observations \citep{transmissionVectors}. 
Although cultural transmission is common in humans, it is also observed in other animals, e.g. chimpanzees \citep{chimpsPrestige, chimpsCopy}, dolphins and whales \citep{dolphins_whales}, elephants \citep{elepahntsRepo}, and even flies \citep{fliesPaper} and fish \citep{Truskanov2020}.

Cultural transmission may combine vertical transmission, in which parents transmit to their offspring; oblique transmission, in which adults (teachers, leaders, strangers) transmit traits to unrelated offspring; and horizontal transmission, in which peers from the same age cohort transmit to one another \citep{transmissionVectorsBook,transmissionVectors}.
It has been demonstrated that non-vertical cultural transmission can maintain maladaptive traits, which can be beneficial in changing environments \citep{changeEnv}.

Transmission biases may cause a cultural trait to have a disproportionate probability to be transmitted compared to its frequency in the population.
Importantly, even when a trait is disfavored by natural selection, it may still spread in a population due to transmission biases that are strong enough to overcome selection \citep[Ch.~8, pg.~279]{evolutionBook}. 
For example, \citet{cooperation} have shown that helping behaviors can evolve due to horizontal transmission bias even without any benefit to the recipient, or when the benefit is much larger than the cost.

% TODO add definition of success bias and some reference to a study demonstrating it in humans or other animals.
Indeed, in a tournament between learning strategies conducted by \citet{strategiesPaper}, most winner strategies included a mixture of success-biased social learning and individual learning, implying that success-biased learning is a good strategy, but that by itself it is not enough, % TODO enough for what?
even if success is measured accurately.

\citet[Ch.~5]{evolutionBook} have suggested that the evaluation of success can be divided into three groups: \emph{direct bias}, \emph{indirect bias} and \emph{frequency-dependent bias}.
A direct bias occurs when one phenotype is more attractive than other phenotypes, and is evaluated by \emph{directly} testing the trait.
For example, an individual observing a ping-pong match can attempt the observed paddle grips to determine which grip is better.
An indirect bias occurs when an individual uses one phenotype to determine the attractiveness of another phenotype.
For example, an observer may copy the paddle grip of the ping-pong player who scored more points in the match, thus indirectly evaluating the grip by the points scored.
This, however, may cause mismatches between the copied trait and the rest of the cultural or genetic repertoire of the individual \citep{Kolodny2022}.
A frequency-dependent bias occurs when the probability to copy a phenotype is higher or lower than the frequency of the phenotype among demonstrators. 
For example, suppose the common paddle grip is used by 60\% of the demonstrators; if the this grip is adopted by 80\% of copiers, then transmission is under positive frequency bias, also called \emph{conformity}; if it is adopted by 40\% of copiers, then transmission is under negative frequency bias, or \emph{non-conformity} \citep{conformism}. 
The effects of conformity and non-conformity on cultural evolution have been studied with both models \citep{anticonformity,Denton2021,conformity} and experiments \citep{negativeFrequency}.

%\paragraph{Prestige.}
Prestige is defined as the ``widespread respect and admiration felt for someone or something on the basis of a perception of their achievements or quality'' (New Oxford American Dictionary).
Therefore, prestige does not directly signify success, although it may imply it--making it an indirect bias.
\citet[Ch.~8]{evolutionBook} and \citet{complexityPaper} suggest that prestige biases are probably more common in humans than success biases.
\citet[Ch. 8]{evolutionBook} add that maladaptive traits may spread widely in a population if indirect biases are strong enough.
They suggest that such biases could lead to a runaway process caused by a cultural equivalent of sexual selection \citep{sexualSelectionBook}.
On the other hand, \citet{fijian_social_bias} suggest that prestige biases, over generations, can lead to cultural adaptations, and that although prestige can lead to maladaptive traits spreading in the population, it can also accelerate the spread of adaptive traits.
Prestige is often mentioned in the cultural evolution literature, but seldom modeled.

%\paragraph{Influence bias.}
Today, social media provides an easy way to estimate the social and cultural influence individuals have over others, and therefore may have an effect on decision making. Online social networks such as \emph{Facebook} and \emph{Instagram} are known to affect the influence of individuals \citep{social_influence,social_media,influence_analysis}, and specific marketing practices were invented to capitalize on this effect \citep{facebook_marketing}.
Here, we model such influence as an indirect bias in cultural transmission, in which the choice of a role-model depends on the choices made by other individuals that have already chosen a role-model. 
Influence can be easily estimated, so costs may be lower than estimating success. In some cases it could be a more accurate estimation as well.

@@

\subsection*{Dichotomous trait}
To allow for mathematical analysis of the model, we introduce a simplified version where the trait only has two phenotypes: the optimal phenotype $\hat{A}$ and the sub-optimal phenotype $A$. 
All role-models with the same phenotype will contribute to the probability of that phenotype to be transmitted, and thus influence is determined by the number of copiers that have already chosen a role-model with either phenotype.
In addition, we assume homogeneous $\alpha$, also called \emph{exchangability}, for simplicity and for easier mathematical analysis.
Therefore, the probability of the $i$-th copier to copy phenotype $A$ is
\begin{equation}\label{eq:binary-model}
G_{i,A} = \frac{(N-C)\alpha'\beta(A) + K_{i,A}}{i-1 + (N-C)\alpha'\beta(A) + C\alpha'\beta(\hat{A})} = \frac{(N-C)\alpha'\beta(A) + K_{i,A}}{i-1 + (N-C)\alpha'\beta(A) + \alpha'C}
\end{equation}
where $C$ is the number of role-models with trait $\hat{A}$ and $K_{i,A}$ is the number of copiers that already chose $A$ when copier $i$ chooses a role-model and $\alpha'$ is the odd ratio of the bias weight $\alpha'= \frac{\alpha}{1-\alpha}$.

@@

\begin{result}[P{\'{o}}lya urn model]\label{result:polya}
The role-model choice process, $\big\{\vec{K}_i\big\}_{i=1}^N$, is equivalent to a \emph{P\'{o}lya urn model} if both trait estimation error and bias weight are uniform in the population, $e=e_j$ and $\alpha=\alpha_j$ for all $j=1,\ldots,N$.
\end{result}

@@

\citet[section 2]{dirichlet} prove that the proportion of different colored balls in a \emph{P\'{o}lya urn model} converges to the Dirichlet distribution as the number of draws approaches infinity, based on the \emph{Martingale Convergence Theorem} \citep{martingaleBook}.
We therefore have an approximation for the relative prestige each role-model has when evaluated by copiers. Thus, choosing the role-models for all copiers is equivalent to drawing from a Multinomial distribution where the parameters are the modified weights from a Dirichlet distribution and we have the following corollary.
\\

\begin{corollary}\label{cor:dirichlet}
The number of copiers of each role-model follows a Dirichlet-Multinomial distribution, $\vec{K_i} \sim \emph{DM}(N,\vec{G_1})$, under the conditions of \Cref{result:polya}.
\end{corollary}

@@

We ran simulations of the role-model choice process during a single generation in which every copier evaluates its own optimal success-bias weight, $\alpha^*$, which minimizes the expected squared error between the estimated and the ideal trait values,
\begin{equation}
\alpha^* = \emph{argmin} \sum_{j=1}^N\frac{\alpha A_j + (1-\alpha) K_j}{\sum_{l=1}^N\alpha A_l + (1-\alpha) K_l}\cdot (\hat{A}-A_j)^2 \;,
\end{equation}
where $A_j$ is the trait of role-model $j$ and $K_j$ the number of copiers that already chose role-model $j$.

@@

\section*{Discussion}
During cultural transmission, cultural traits such as attitudes, values, beliefs, and behavioral patterns are transmitted between individuals, for example via copying and social learning.
Some cultural traits or cultural role-models may be copied more often due to transmission biases. 
A common bias is success bias, in which copiers are more likely to copy a successful role-model. Many models assume that success can be accurately estimated.
However, it has been suggested that because it is hard to estimate success, a more common bias is \emph{prestige bias}---a bias towards role-models perceived to be successful in other traits \citep{fijian_social_bias}.

@@

According to \citet{animal_leadership}, there are two main approaches to group decision making in nature: leadership and consensus.
Leaders would usually be high-ranking members of the group: elders, individuals with many kin relations, or individuals possessing other dominant traits.
\citet{animal_leadership} describe benefits for the closest associates of a dominant baboon, such as protection from predators. 
In some species, like the females of \emph{Eulemur fulvus rufus} (Red lemur), leaders may arise due to nutritional needs, and not due to possessing superior traits \citep{lemurs}. 
In humans, leadership also has its costs and benefits. Leaders can make decisions that would most benefit them and their closest followers, while still maintaining group cohesion. 
However, wrong decision making that harms the group could result in negative effects for the leader. 
In modern society, many humans strive for prestigious positions, as they may reap rewards greater than the risk and costs to achieve them, or due to individual personality and pressure or education from the family.

\citet{prestige_evolution} suggested that there are two types of leadership: prestige-based and dominance-based leadership.
In the latter, social status is acquired through aggression, intimidation and violence. It is also more common than prestige in non-human animals.
Their definition of prestige seems to overlap with ours. They suggest prestige is composed of estimation in the eyes of other people (similar to our success bias) and commanding position in people's minds, i.e, the number of followers other people think one has, which they define as \emph{influence}, similar to our influence bias.
\citet{prestige_evolution} show that prestige can evolve via natural selection as an efficient process to extract reproductive benefit from the flow of socially transmitted information. They back up their claims by creating testable predictions and using evidence from the literature and experiments of social sciences.
Simply put, prestige can naturally evolve when social learning already exists to save costs of individual learning.

@@

Prestige bias can also accelerate reversal of harmful traditions such as child marriage and domestic violence. 
\citet{harmful_traditions} suggest a \emph{spillover}  mechanism, in which an intervention affects a large enough group in a target population, so that others not included in the intervention also change their behavior.
They found that there are individuals who act as \emph{agents}, who are often looked upon, and therefore they are ideal targets for interventions. This is similar to influential role-models in our model, where a prestigious individual will be copied more often, and will therefore spread his trait faster and wider in the population.
They also suggest a way to use this phenomena to change existing traditions in a population. It is very clear however, that just as it can be used to end harmful traditions, the same agents could start harmful traditions.

\citet{social_brains} hypothesized that larger, more complex brains can store and manage more information and in turn, this information can support the costs of a larger brain.
Following up on this, \citet{collective_brains} offered that prestige can directly affect human physical evolution. They present a concept called \emph{cultural brains}---brains that evolved primarily for the acquisition of adaptive knowledge.
They then develop a model that predicts a strong relationship between brain size and group size, because group size also provides access to more adaptive knowledge. 
They also presented the \emph{cumulative cultural brain} hypothesis, which proposes that human brains have evolved with an ability and tendency for selective, high-fidelity social learning. As part of this process, there are a variety of strategies and biases that have evolved to hone in on the most adaptive knowledge. These strategies and biases include direct and indirect cues of the popularity of cultural traits (e.g. success and prestige biases).
They suggest that one of the reasons for the extreme increase in brain size in humans is the ability to "cheaply" acquire adaptive knowledge via transmission biases such as prestige.
